Data analysis

### 2025-04-11 processing/02-analysis.qmd
Update analysis and repo order

@@

```{r}
#| label: tbl-summary
#| tbl-cap: "Estadísticos descriptivos"
#| tbl-cap-location: top
t1 <- df_study1_long_t7 %>% 
  select(just_health, just_pension, just_educ, mjp, perc_inequality, just_inequality, merit_effort, merit_talent, ess, ideo, educ, sex, age)

@@

@@

datos.health <- df_study1_long_t7 %>% 
  group_by(idencuesta, ola) %>% 
  count(just_health) %>% 
  group_by(ola) %>% 
  mutate(porcentaje=n/sum(n)) %>% 
  ungroup() %>% 
  na.omit() %>% 
  mutate(wave = case_when(ola == 1 ~ "2016",
                          ola == 2 ~ "2017",
                          ola == 3 ~ "2018",
                          ola == 4 ~ "2019",
                          ola == 6 ~ "2022",
                          ola == 7 ~ "2023"),
         wave = factor(wave, levels = c("2016",
                                      "2017",
                                      "2018",
                                      "2019",
                                      "2022",
                                      "2023")))

etiquetas.health <- df_study1_long_t7 %>%
  group_by(ola, just_health) %>%
  summarise(count = n(), .groups = "drop") %>%
  group_by(ola) %>%
  mutate(porcentaje = count / sum(count)) %>% 
  na.omit() %>% 
  mutate(idencuesta = 1,
         wave = case_when(ola == 1 ~ "2016",
                          ola == 2 ~ "2017",
                          ola == 3 ~ "2018",
                          ola == 4 ~ "2019",
                          ola == 6 ~ "2022",
                          ola == 7 ~ "2023"),
         wave = factor(wave, levels = c("2016",
                                        "2017",
                                        "2018",
                                        "2019",
                                        "2022",
                                        "2023")))

p1 <- datos.health %>% 
  ggplot(aes(x = wave, fill = just_health, stratum = just_health,
             alluvium = idencuesta, y = porcentaje)) +
  ggalluvial::geom_flow(alpha = .4) + 
  ggalluvial::geom_stratum(linetype = 0) +
  scale_y_continuous(labels = scales::percent) + 
  scale_fill_manual(values =  c("#CA0020","#F4A582","#b3b3b3ff","#92C5DE","#0571B0")) +
  geom_shadowtext(data = etiquetas.health,
                  aes(label = ifelse(porcentaje > 0 , scales::percent(porcentaje, accuracy = .1),"")),
                  position = position_stack(vjust = .5),
                  show.legend = FALSE,
                  size = 3,
                  color = rep('white'),
                  bg.colour='grey30')+
  labs(y = "%",
       x = NULL,
       fill = NULL,
       title = "a. Health") +
  theme_ggdist() +
  theme(legend.position = "none")

datos.pension <- df_study1_long_t7 %>% 
  group_by(idencuesta, ola) %>% 
  count(just_pension) %>% 
  group_by(ola) %>% 
  mutate(porcentaje=n/sum(n)) %>% 
  ungroup() %>% 
  na.omit() %>% 
  mutate(wave = case_when(ola == 1 ~ "2016",
                          ola == 2 ~ "2017",
                          ola == 3 ~ "2018",
                          ola == 4 ~ "2019",
                          ola == 6 ~ "2022",
                          ola == 7 ~ "2023"),
         wave = factor(wave, levels = c("2016",
                                        "2017",
                                        "2018",
                                        "2019",
                                        "2022",
                                        "2023")))

etiquetas.pension <- df_study1_long_t7 %>%
  group_by(ola, just_pension) %>%
  summarise(count = n(), .groups = "drop") %>%
  group_by(ola) %>%
  mutate(porcentaje = count / sum(count)) %>% 
  na.omit() %>% 
  mutate(idencuesta = 1,
         wave = case_when(ola == 1 ~ "2016",
                          ola == 2 ~ "2017",
                          ola == 3 ~ "2018",
                          ola == 4 ~ "2019",
                          ola == 6 ~ "2022",
                          ola == 7 ~ "2023"),
         wave = factor(wave, levels = c("2016",
                                        "2017",
                                        "2018",
                                        "2019",
                                        "2022",
                                        "2023")))

p2 <- datos.pension %>% 
  ggplot(aes(x = wave, fill = just_pension, stratum = just_pension,
             alluvium = idencuesta, y = porcentaje)) +
  ggalluvial::geom_flow(alpha = .4) + 
  ggalluvial::geom_stratum(linetype = 0) +
  scale_y_continuous(labels = scales::percent) + 
  scale_fill_manual(values =  c("#CA0020","#F4A582","#b3b3b3ff","#92C5DE","#0571B0")) +
  geom_shadowtext(data = etiquetas.pension,
                  aes(label = ifelse(porcentaje > 0 , scales::percent(porcentaje, accuracy = .1),"")),
                  position = position_stack(vjust = .5),
                  show.legend = FALSE,
                  size = 3,
                  color = rep('white'),
                  bg.colour='grey30')+
  labs(y = "%",
       x = NULL,
       fill = NULL,
       title = "b. Pension") +
  theme_ggdist() +
  theme(legend.position = "none")

datos.educ <- df_study1_long_t7 %>% 
  group_by(idencuesta, ola) %>% 
  count(just_educ) %>% 
  group_by(ola) %>% 
  mutate(porcentaje=n/sum(n)) %>% 
  ungroup() %>% 
  na.omit() %>% 
  mutate(wave = case_when(ola == 1 ~ "2016",
                          ola == 2 ~ "2017",
                          ola == 3 ~ "2018",
                          ola == 4 ~ "2019",
                          ola == 6 ~ "2022",
                          ola == 7 ~ "2023"),
         wave = factor(wave, levels = c("2016",
                                        "2017",
                                        "2018",
                                        "2019",
                                        "2022",
                                        "2023")))

etiquetas.educ <- df_study1_long_t7 %>%
  group_by(ola, just_educ) %>%
  summarise(count = n(), .groups = "drop") %>%
  group_by(ola) %>%
  mutate(porcentaje = count / sum(count)) %>% 
  na.omit() %>% 
  mutate(idencuesta = 1,
         wave = case_when(ola == 1 ~ "2016",
                          ola == 2 ~ "2017",
                          ola == 3 ~ "2018",
                          ola == 4 ~ "2019",
                          ola == 6 ~ "2022",
                          ola == 7 ~ "2023"),
         wave = factor(wave, levels = c("2016",
                                        "2017",
                                        "2018",
                                        "2019",
                                        "2022",
                                        "2023")))

p3 <- datos.educ %>% 
  ggplot(aes(x = wave, fill = just_educ, stratum = just_educ,
             alluvium = idencuesta, y = porcentaje)) +
  ggalluvial::geom_flow(alpha = .4) + 
  ggalluvial::geom_stratum(linetype = 0) +
  scale_y_continuous(labels = scales::percent) + 
  scale_fill_manual(values =  c("#CA0020","#F4A582","#b3b3b3ff","#92C5DE","#0571B0")) +
  geom_shadowtext(data = etiquetas.educ,
                  aes(label = ifelse(porcentaje > 0 , scales::percent(porcentaje, accuracy = .1),"")),
                  position = position_stack(vjust = .5),
                  show.legend = FALSE,
                  size = 3,
                  color = rep('white'),
                  bg.colour='grey30')+
  labs(y = "%",
       x = NULL,
       fill = NULL,
       title = "c. Education") +
  theme_ggdist() +
  theme(legend.position = "bottom")

@@

@@

```{r}
df_study1_long_t7 %>%
  filter(ola == 7) %>% 
  select(mjp, perc_inequality, just_inequality, merit_effort, merit_talent) %>% 
  mutate_all(.funs = ~ as.numeric(.)) %>% 
  sjPlot::tab_corr(., triangle = "lower")
```

@@

```{r}
# Generate analytical sample

df_study1 <- df_study1_long_t7 %>%
  select(idencuesta,
         ola,
         ponderador_long_total,
         mjp, 
         perc_inequality, 
         just_inequality,
         merit_effort, 
         merit_talent, 
         educ,
         quintil1,
         sex,
         age,
         ess, 
         ideo) %>% 
  na.omit() %>% 
  mutate(ola = as.factor(ola),
         ola_num = as.numeric(ola),
         ola_2=as.numeric(ola)^2)

@@

m9 <- lmer(mjp ~ 1 + ola_num + ola_2 + perc_inequality*ola_num + just_inequality + merit_effort + merit_talent + perc_inequality_mean + just_inequality_mean + merit_effort_mean + merit_talent_mean + educ + quintil1 + ess + ideo + sex + age + (1 + ola_num | idencuesta),
                data = df_study1)

m10 <- lmer(mjp ~ 1 + ola_num + ola_2 + perc_inequality*ola_num + just_inequality*ola_num + merit_effort + merit_talent + perc_inequality_mean + just_inequality_mean + merit_effort_mean + merit_talent_mean + educ + quintil1 + ess + ideo + sex + age + (1 + ola_num | idencuesta),
                data = df_study1)

m11 <- lmer(mjp ~ 1 + ola_num + ola_2 + perc_inequality*ola_num + just_inequality*ola_num + merit_effort*ola_num + merit_talent + perc_inequality_mean + just_inequality_mean + merit_effort_mean + merit_talent_mean + educ + quintil1 + ess + ideo + sex + age + (1 + ola_num | idencuesta),
                data = df_study1)

m12 <- lmer(mjp ~ 1 + ola_num + ola_2 + perc_inequality*ola_num + just_inequality*ola_num + merit_effort*ola_num + merit_talent*ola_num + perc_inequality_mean + just_inequality_mean + merit_effort_mean + merit_talent_mean + educ + quintil1 + ess + ideo + sex + age + (1 + ola_num | idencuesta),
                data = df_study1)
```

>>>>

# Generate analytical sample

df_study1 <- df_study1_long_t7 %>%
  select(idencuesta,
         ola,
         ponderador_long_total,
         segmento,
         estrato,
         just_health,
         just_pension,
         just_educ,
         mjp, 
         perc_inequality, 
         just_inequality,
         merit_effort, 
         merit_talent, 
         educ,
         quintil1,
         sex,
         age,
         ess, 
         ideo) %>% 
  na.omit() %>% 
  mutate(ola = as.factor(ola),
         ola_num = as.numeric(ola),
         ola_2=as.numeric(ola)^2)

# Corregir etiquetas

df_study1$just_health <- sjlabelled::set_label(df_study1$just_health, 
                        label = "Health distributive justice")

df_study1$just_pension <- sjlabelled::set_label(df_study1$just_pension, 
                        label = "Pension distributive justice")

df_study1$just_educ <- sjlabelled::set_label(df_study1$just_educ, 
                        label = "Education distributive justice")

df_study1$merit_effort <- sjlabelled::set_label(df_study1$merit_effort, 
                        label = "People are rewarded for their efforts")

df_study1$merit_talent <- sjlabelled::set_label(df_study1$merit_talent, 
                        label = "People are rewarded for their intelligence")

@@

```{r}
#| label: tbl-summary1
#| tbl-cap: "Estadísticos descriptivos items justicia de mercado"
#| tbl-cap-location: top
t1 <- df_study1 %>% 
  filter(ola == 1) %>% 
  select(just_health, just_pension, just_educ, mjp)

@@

```{r}
#| label: tbl-summary2
#| tbl-cap: "Estadísticos descriptivos variables independientes"
#| tbl-cap-location: top
t2 <- df_study1 %>% 
  filter(ola == 1) %>% 
  select(perc_inequality, just_inequality, merit_effort, merit_talent)

print(summarytools::dfSummary(t2), method="render")
```

@@

datos.health <- df_study1 %>% 
  mutate(just_health = factor(just_health, 
                              levels = c("Strongly agree",
                                         "Agree",
                                         "Neither agree nor desagree",
                                         "Desagree",
                                         "Strongly desagree"))) %>% 
  group_by(idencuesta, ola) %>% 
  count(just_health) %>% 
  group_by(ola) %>% 
  mutate(porcentaje=n/sum(n)) %>% 
  ungroup() %>% 
  na.omit() %>% 
  mutate(wave = case_when(ola == 1 ~ "2016",
                          ola == 2 ~ "2017",
                          ola == 3 ~ "2018",
                          ola == 4 ~ "2019",
                          ola == 6 ~ "2022",
                          ola == 7 ~ "2023"),
         wave = factor(wave, levels = c("2016",
                                      "2017",
                                      "2018",
                                      "2019",
                                      "2022",
                                      "2023")))

etiquetas.health <- df_study1 %>%
  mutate(just_health = factor(just_health, 
                              levels = c("Strongly agree",
                                         "Agree",
                                         "Neither agree nor desagree",
                                         "Desagree",
                                         "Strongly desagree"))) %>% 
  group_by(ola, just_health) %>%
  summarise(count = n(), .groups = "drop") %>%
  group_by(ola) %>%
  mutate(porcentaje = count / sum(count)) %>% 
  na.omit() %>% 
  mutate(idencuesta = 1,
         wave = case_when(ola == 1 ~ "2016",
                          ola == 2 ~ "2017",
                          ola == 3 ~ "2018",
                          ola == 4 ~ "2019",
                          ola == 6 ~ "2022",
                          ola == 7 ~ "2023"),
         wave = factor(wave, levels = c("2016",
                                        "2017",
                                        "2018",
                                        "2019",
                                        "2022",
                                        "2023")))

p1 <- datos.health %>% 
  ggplot(aes(x = wave, fill = just_health, stratum = just_health,
             alluvium = idencuesta, y = porcentaje)) +
  ggalluvial::geom_flow(alpha = .4) + 
  ggalluvial::geom_stratum(linetype = 0) +
  scale_y_continuous(labels = scales::percent) + 
  scale_fill_manual(values =  c("#0571B0","#92C5DE","#b3b3b3ff","#F4A582","#CA0020")) +
  geom_shadowtext(data = etiquetas.health,
                  aes(label = ifelse(porcentaje > 0 , scales::percent(porcentaje, accuracy = .1),"")),
                  position = position_stack(vjust = .5),
                  show.legend = FALSE,
                  size = 3,
                  color = rep('white'),
                  bg.colour='grey30')+
  labs(y = "%",
       x = NULL,
       fill = NULL,
       title = "a. Health") +
  theme_ggdist() +
  theme(legend.position = "none")

datos.pension <- df_study1 %>% 
   mutate(just_pension = factor(just_pension, 
                              levels = c("Strongly agree",
                                         "Agree",
                                         "Neither agree nor desagree",
                                         "Desagree",
                                         "Strongly desagree"))) %>% 
  group_by(idencuesta, ola) %>% 
  count(just_pension) %>% 
  group_by(ola) %>% 
  mutate(porcentaje=n/sum(n)) %>% 
  ungroup() %>% 
  na.omit() %>% 
  mutate(wave = case_when(ola == 1 ~ "2016",
                          ola == 2 ~ "2017",
                          ola == 3 ~ "2018",
                          ola == 4 ~ "2019",
                          ola == 6 ~ "2022",
                          ola == 7 ~ "2023"),
         wave = factor(wave, levels = c("2016",
                                        "2017",
                                        "2018",
                                        "2019",
                                        "2022",
                                        "2023")))

etiquetas.pension <- df_study1 %>%
  mutate(just_pension = factor(just_pension, 
                              levels = c("Strongly agree",
                                         "Agree",
                                         "Neither agree nor desagree",
                                         "Desagree",
                                         "Strongly desagree"))) %>% 
  group_by(ola, just_pension) %>%
  summarise(count = n(), .groups = "drop") %>%
  group_by(ola) %>%
  mutate(porcentaje = count / sum(count)) %>% 
  na.omit() %>% 
  mutate(idencuesta = 1,
         wave = case_when(ola == 1 ~ "2016",
                          ola == 2 ~ "2017",
                          ola == 3 ~ "2018",
                          ola == 4 ~ "2019",
                          ola == 6 ~ "2022",
                          ola == 7 ~ "2023"),
         wave = factor(wave, levels = c("2016",
                                        "2017",
                                        "2018",
                                        "2019",
                                        "2022",
                                        "2023")))

p2 <- datos.pension %>% 
  ggplot(aes(x = wave, fill = just_pension, stratum = just_pension,
             alluvium = idencuesta, y = porcentaje)) +
  ggalluvial::geom_flow(alpha = .4) + 
  ggalluvial::geom_stratum(linetype = 0) +
  scale_y_continuous(labels = scales::percent) + 
  scale_fill_manual(values =  c("#0571B0","#92C5DE","#b3b3b3ff","#F4A582","#CA0020")) +
  geom_shadowtext(data = etiquetas.pension,
                  aes(label = ifelse(porcentaje > 0 , scales::percent(porcentaje, accuracy = .1),"")),
                  position = position_stack(vjust = .5),
                  show.legend = FALSE,
                  size = 3,
                  color = rep('white'),
                  bg.colour='grey30')+
  labs(y = "%",
       x = NULL,
       fill = NULL,
       title = "b. Pension") +
  theme_ggdist() +
  theme(legend.position = "none")

datos.educ <- df_study1 %>% 
  mutate(just_educ = factor(just_educ, 
                              levels = c("Strongly agree",
                                         "Agree",
                                         "Neither agree nor desagree",
                                         "Desagree",
                                         "Strongly desagree"))) %>%
  group_by(idencuesta, ola) %>% 
  count(just_educ) %>% 
  group_by(ola) %>% 
  mutate(porcentaje=n/sum(n)) %>% 
  ungroup() %>% 
  na.omit() %>% 
  mutate(wave = case_when(ola == 1 ~ "2016",
                          ola == 2 ~ "2017",
                          ola == 3 ~ "2018",
                          ola == 4 ~ "2019",
                          ola == 6 ~ "2022",
                          ola == 7 ~ "2023"),
         wave = factor(wave, levels = c("2016",
                                        "2017",
                                        "2018",
                                        "2019",
                                        "2022",
                                        "2023")))

etiquetas.educ <- df_study1 %>%
    mutate(just_educ = factor(just_educ, 
                              levels = c("Strongly agree",
                                         "Agree",
                                         "Neither agree nor desagree",
                                         "Desagree",
                                         "Strongly desagree"))) %>%
  group_by(ola, just_educ) %>%
  summarise(count = n(), .groups = "drop") %>%
  group_by(ola) %>%
  mutate(porcentaje = count / sum(count)) %>% 
  na.omit() %>% 
  mutate(idencuesta = 1,
         wave = case_when(ola == 1 ~ "2016",
                          ola == 2 ~ "2017",
                          ola == 3 ~ "2018",
                          ola == 4 ~ "2019",
                          ola == 6 ~ "2022",
                          ola == 7 ~ "2023"),
         wave = factor(wave, levels = c("2016",
                                        "2017",
                                        "2018",
                                        "2019",
                                        "2022",
                                        "2023")))

p3 <- datos.educ %>% 
  ggplot(aes(x = wave, fill = just_educ, stratum = just_educ,
             alluvium = idencuesta, y = porcentaje)) +
  ggalluvial::geom_flow(alpha = .4) + 
  ggalluvial::geom_stratum(linetype = 0) +
  scale_y_continuous(labels = scales::percent) + 
  scale_fill_manual(values =  c("#0571B0","#92C5DE","#b3b3b3ff","#F4A582","#CA0020")) +
  geom_shadowtext(data = etiquetas.educ,
                  aes(label = ifelse(porcentaje > 0 , scales::percent(porcentaje, accuracy = .1),"")),
                  position = position_stack(vjust = .5),
                  show.legend = FALSE,
                  size = 3,
                  color = rep('white'),
                  bg.colour='grey30')+
  labs(y = "%",
       x = NULL,
       fill = NULL,
       title = "c. Education",
       caption = "Source: own elaboration with pooled data from ELSOC 2016-2023 (n = 8460)") +
  theme_ggdist() +
  theme(legend.position = "bottom")

@@

```{r}
library(srvyr)

df_pond <- df_study1 %>% 
  mutate(ola = case_when(ola == 1 ~ "2016",
                         ola == 2 ~ "2017",
                         ola == 3 ~ "2018",
                         ola == 4 ~ "2019",
                         ola == 6 ~ "2022",
                         ola == 7 ~ "2023"),
         ola = factor(ola, levels = c("2016",
                                        "2017",
                                        "2018",
                                        "2019",
                                        "2022",
                                        "2023"))) %>% 
  as_survey_design(.data = .,
                   ids = segmento, 
                   strata = estrato, 
                   weights = ponderador_long_total)

df_pond %>% 
  select(ola, mjp, perc_inequality, just_inequality, merit_effort, merit_talent) %>% 
  mutate_at(.vars = 2:6, .funs = ~ as.numeric(.)) %>% 
  group_by(ola) %>% 
  summarise_all(~survey_mean(., vartype = "ci")) %>% 
  pivot_longer(cols = -ola,
               names_to = "temp",
               values_to = "valor") %>%
  mutate(
    ci = case_when(
      str_ends(temp, "_low") ~ "ic_low",
      str_ends(temp, "_upp") ~ "ic_upp",
      TRUE                   ~ "mean"
    ),
    variable = str_remove(temp, "_low|_upp")
  ) %>%
  select(ola, variable, ci, valor) %>%
  pivot_wider(
    names_from  = ci,
    values_from = valor
  ) %>% 
  mutate(variable = case_when(variable == "mjp" ~ "Market justice preferences",
                              variable == "perc_inequality"  ~ "Inequality perception",
                              variable == "just_inequality"  ~ "Inequality justification",
                              variable == "merit_effort"     ~ "Merit: Effort",
                              variable == "merit_talent"     ~ "Merit: Talent"),
         variable = factor(variable, levels = c("Market justice preferences",
                                      "Inequality perception",
                                      "Inequality justification",
                                      "Merit: Effort",
                                      "Merit: Talent")
                              )) %>% 
  ggplot(aes(x = ola, y = mean, group = variable)) +
  geom_point(aes(shape=variable, color=variable), size = 3.5) +
  geom_line(aes(color = variable), linewidth = 0.8) +
  geom_errorbar(aes(ymin = ic_low, ymax = ic_upp, color = variable),
                width = 0.1) +
  scale_color_manual(values = c("#023858", # azul oscuro
                                "#0571B0", # azul intermedio
                                "#b3b3b3", # gris
                                "#F4A582", # salmón
                                "#B2182B"  # rojo profundo
                                         )) +
  scale_shape_manual(values=c(15, 16, 17, 18, 4)) +
  labs(y = "Mean",
       x = NULL,
       color = NULL,
       shape = NULL,
       caption = "Source: own elaboration with pooled data from ELSOC 2016-2023 (n = 8460)") +
  theme_ggdist() +
  theme(legend.position = "top",
        text = element_text(size = 12))

@@

```{r}
M <- df_study1 %>%
  filter(ola == 7) %>% 
  select(mjp, perc_inequality, just_inequality, merit_effort, merit_talent) %>% 
  mutate_all(.funs = ~ as.numeric(.)) %>% 
  cor(use = "pairwise.complete.obs", method = "pearson")

diag(M) <- NA

rownames(M) <- c("A. Marjet justice preferences",
                 "B. Inequality gap perception",
                 "C. Inequality gap justification",
                 "D. People are rewarded for their efforts ",
                 "E. People are rewarded for their intelligence")

#set Column names of the matrix
colnames(M) <-c("(A)", "(B)","(C)","(D)","(E)")

#Plot the matrix using corrplot
corrplot::corrplot(M,
                   method = "color",
                   addCoef.col = "black",
                   type = "upper",
                   tl.col = "black",
                   col = colorRampPalette(c("#E16462", "white", "#0D0887"))(12),
                   bg = "white",
                   na.label = "-")

@@

```{r}

@@

m9 <- lmer(mjp ~ 1 + ola_num + ola_2 + perc_inequality*ola_num + just_inequality + merit_effort + merit_talent + perc_inequality_mean + just_inequality_mean + merit_effort_mean + merit_talent_mean + educ + quintil1 + ess + ideo + sex + age + (1 + perc_inequality | idencuesta),
                data = df_study1)

m10 <- lmer(mjp ~ 1 + ola_num + ola_2 + perc_inequality + just_inequality*ola_num + merit_effort + merit_talent + perc_inequality_mean + just_inequality_mean + merit_effort_mean + merit_talent_mean + educ + quintil1 + ess + ideo + sex + age + (1 + just_inequality| idencuesta),
                data = df_study1)

m11 <- lmer(mjp ~ 1 + ola_num + ola_2 + perc_inequality + just_inequality + merit_effort*ola_num + merit_talent + perc_inequality_mean + just_inequality_mean + merit_effort_mean + merit_talent_mean + educ + quintil1 + ess + ideo + sex + age + (1 + merit_effort | idencuesta),
                data = df_study1)

m12 <- lmer(mjp ~ 1 + ola_num + ola_2 + perc_inequality + just_inequality + merit_effort + merit_talent*ola_num + perc_inequality_mean + just_inequality_mean + merit_effort_mean + merit_talent_mean + educ + quintil1 + ess + ideo + sex + age + (1 + merit_talent | idencuesta),
                data = df_study1)
```
